---
title: "ip_week12"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# **AD CLICK ANALYSIS**
# Defining the Question
## 1. Specifying the Question
### Which individuals are most likely to click on an online cryptography course advertisement?

## 2. Metric for success
### Come up with an analysis that will make our customer identify individuals who are likely to click on her cryptography course.

## 3. Understanding the Context
### A Kenyan entrepreneur has created an online cryptography course and would want to advertise it on her blog. She currently targets audiences originating from various countries. In the past, she ran ads to advertise a related course on the same blog and collected data in the process. She would now like to employ your services as a Data Science Consultant to help her identify which individuals are most likely to click on her ads.

## 4. Experimental Design taken
1. Data Exploration
2. Data Cleaning 
3. Univariate Analysis
4. Bivariate Analysis
5. Conclusion 

## 5. Appropriateness data 
### Our data was readily available as it was provided by the client...Thus data collection was not needed.

# 1. Data Exploration
## Loading the data
## Loading the necessary packages
``` {r}
library("data.table")
advert <- read.csv("advertising.csv")

##Previewing the first 6 rows of dataset

head(advert)

##Previewing the last 6 rows of dataset

tail(advert)

##Basic structure of the data
str(advert)
```

# 2. Data Cleaning 
## Tidying the dataset the dataset

``` {r}
# Identifying duplicates
advert[duplicated(advert), ]

##There are no duplicates in this dataset.

## Identifying missing data
length(which(!is.na(advert)))
#
##checking the missing data
colSums(is.na(advert))

##There is no missing data
```
## Checking for outliers

``` {r}
boxplot.stats(advert$`Daily Time Spent on Site`)$out

boxplot.stats(advert$Age)$out

boxplot.stats(advert$`Area Income`)$out

boxplot.stats(advert$`Daily Internet Usage`)$out

boxplot.stats(advert$`Clicked on Ad`)$out
```

``` {r}
numeric_cols <- unlist(lapply(advert, is.numeric)) 
numeric_cols

boxplot(numeric_cols)
``` 
we do not have outliers.

## checking for anomalies
Anomalies are inconsistencies in the data

``` {r}
###Checking the number of unique values in each column
lengths(lapply(advert, unique))
str(advert)
```

# 3. Univariate Analysis
## checking the means of all our numerical values

``` {r}
# Summary of the dataset
summary(advert)
```

``` {r}
# Getting the time period of the data
range(advert$Timestamp)
```

### Getting variance and std.deviation of Daily time spent on site

``` {r}
advert.daily.variance <- var(advert$Daily.Time.Spent.on.Site)
advert.daily.variance
```

``` {r}
#checking the datatypes on the columns 
sapply(advert, class)
```

``` {r}
# Getting variance and std.deviation of Area Income

var(advert$Area.Income)
```

``` {r}
##the timestamp has  a wrong data type so we will need to convert it to datetime
advert$Timestamp <- as.POSIXct(advert$Timestamp, "%Y-%m-%d %H:%M:%S",tz = "GMT")

### Checking if change has been effected
sapply(advert, class)
```

``` {r}
summary(advert)
```


### Getting variance and std.deviation of Daily time spent on site
``` {r}
var(advert$Daily.Time.Spent.on.Site)

sd(advert$Daily.Time.Spent.on.Site)
```

``` {r}
# Getting variance and std.deviation of Area Income

var(advert$Area.Income)

sd(advert$Area.Income)
```

``` {r}
# Getting variance and std.deviation of Daily Internet Usage
sd(advert$Daily.Internet.Usage)

var(advert$Daily.Internet.Usage)
```

``` {r}
# Function to get mode
mode <- function(v){
  uniq <- unique(as.integer(v))
  uniq[which.max(tabulate(match(as.integer(v), uniq)))]
}
```

``` {r}
# Mode of daily time spent on site
daily.site <- mode(advert$Daily.Time.Spent.on.Site)
daily.site
```
Alot of people spend 78 minutes browsing on the site.

``` {r}
# Getting the mode of the age
age.mode <- mode(advert$Age)
age.mode
```

Most people on the site are age 31
``` {r}
# Distribution of the genders
gender <- advert$Male
gen <- table(gender)
barplot(gen, main = "Gender Distribution", ylab = "Distribution")
```

Females browsing on the site are more than males by a small percantage.
``` {r}
# Distribution of whether one clicked or did not click on an ad
click <- advert$Clicked.on.Ad
clicked <- table(click)
barplot(clicked, main = "Ad Click Distribution", ylab = "Distribution")
```

There is a 50% chance that someone will click on the add while browsing the internet.
``` {r}
area_income_mode<- mode((advert$Area.Income))
area_income_mode
```

``` {r}
internetusage_mode<- mode(advert$Daily.Internet.Usage)
internetusage_mode
```
### range
``` {r}
range(advert$Age)
```

people browsing the internet are between ages 19 an 61.

``` {r}
# ad clicked per country
country_ad <- table(advert$Country, advert$Clicked.on.Ad)
names(dimnames(country_ad)) <- c("Country", "Clicked on Ad")
country_ad
```

People from Australia, Ethopia, turkey and Liechtenstein had highest click on the ad, Liechtenstein and ethopia had all people click on the ad.


# 4. Bivariate Analysis

``` {r}
# Assigning the age column to the variable age
# ---
# 
age <- advert$Age
```

``` {r}
# Assigning the Clicked.on.Ad column to the variable adclicked
# ---
# 
timespent<- advert$ Daily.Time.Spent.on.Site
```

### Using the cov() function to determine the covariance
``` {r}
#
cov(age, timespent)
```

The covariance is a strong negative relatnship between Age and tme spent on sight.
``` {r}
# Using the cor() function to determine the correlation
# ---
#
cor(age, timespent)
```
There is no relationship between age and time spent on site

``` {r}
# Getting correlation of the continuous variables
cor(advert[,unlist(lapply(advert, is.numeric))])
```

### Correlation plot package
``` {r}
#install.packages("corrplot")
library('corrplot')

#Plotting a correlation matrix plot
corrplot(cor(advert[,unlist(lapply(advert, is.numeric))]), type = "upper", order = "hclust", tl.col = "black", tl.srt = 45)
```

``` {r}
#install.packages("tidyverse")

# Grouping the data by whether one clicked an ad or not
group <- NA
group[advert$Clicked.on.Ad == 1] <- 1
group[advert$Clicked.on.Ad == 0] <- 2

# Plotting a pair plot
pairs(advert[,1:4], pch = 19, lower.panel = NULL, 
      main="Pair Plots showing the relationships between variables",
      col = c("red", "purple")[group])
```

``` {r}
# Grouping by gender
group1 <- NA
group1[advert$Male == 1] <- 1
group1[advert$Male == 0] <- 2

# Setting the x and y variables
x <- advert$Age
y <- advert$Daily.Time.Spent.on.Site

# Scatter plot
plot(x, y, xlab = "Age", ylab = "Time Spent on Site", col = c("red", "purple")[group],
     main="Scatter Plot showing age in relation to time spent on Site")
legend("topleft",c("Clicked","Not clicked"), fill=c("red","purple"))
```

Those who are younger than 40 years were more likely to click on an ad. The less the time spent on a site, the more likely one would not click on an ad.

``` {r}
# Setting a new variable 
n <- advert$Daily.Internet.Usage

# Scatter plot
plot(x, n, xlab = "Age", ylab = "Time Spent on Site", col = c("red", "purple")[group1],
     main="Scatter Plot showing age in relation to Internet usage")
legend("topleft",c("Male","Female"), fill=c("red","purple"))
```
Both genders are equally distributed in terms of time spent on site.


### Getting individuals Who are likely to click on the advertisement.
``` {r}
#install.packages("dplyr")
library(dplyr)


head(advert)

filter(advert, Age >= 35 & Daily.Time.Spent.on.Site < 60)
```

# 5. Conclusion


1. 262 individuals who are most likely to click on the ad have been selected.
2. Most individuals who clicked on the ad where below the age of 60.
3. Users who spent less time online were more likely to click on the ad than people who spent more time.
4. People from Australia, Ethopia, turkey and Liechtenstein had highest click on the ad

# 6. Recommendation

1.Client should focus on people who had a higher daily internet usage as they were likely to click on her ads.
2. Client could also try reduce the price of the course, to attract more peoples

